% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
\usepackage{hyperref}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

\begin{document} 

\name{WENZHONG ZHANG\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name      

\address{\bf  Unit 808, 38 Dan Leckie Way\\Toronto, ON M5V 2V6\\(416)
795-0370\\\href{mailto:wenzhong.zhang@mail.utoronto.ca}{wenzhong.zhang@mail.utoronto.ca}}

\begin{resume}

\section{SUMMARY}          
    Moved to Toronto from China in 2007. I love languages, travelling and culture.
    Github page: \url{https://github.com/zhwzh308}.
 
\section{EDUCATION}          
    University of Toronto, Toronto, ON  \\        
    Bachelor of Applied Science, May 2014   \\       
    Computer Engineering       \\   
 
\section{EXPERIENCE}
   \vspace{-0.1in}	
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Component Quality Engineer} \>AMD Incorporated     \>May-Aug 2011/12\\
                             \>Markham, Ontario
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Designed tests for AMD graphics driver, multimedia component.
    Responsible for daily staging test, weekly build promotion.       
    Certified AMD Graphic Driver for docking station used by Sony VAIO Z series laptop.
    Recognition from VP of Sony and VP of AMD
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Build Manager} \>MyBPM tool   \> ~~~~~~ Winter 2014\\
                          \>Software Engineering II course project
   \end{tabbing}\vspace{-20pt}
    Built and deployed the Ruby on Rails application on Amazon Web Service.
    Provided assistance to team members with development associated issues.
    Developed with front end team using JavaScript (JQuery, Raphael).
    Styled website using Bootstrap. Project is available at \linebreak
    \url{http://www.mybpmtool.com/}
   \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
   {\bf Developer}  \>Real-time Bloodflow Simulator \> Sep.-April, 2013/14\\
                          \>Capstone Project
   \end{tabbing}\vspace{-20pt}
    Implemented image processing framework.          
    Responsible for implementing skin detection, skin segmentation and post-processing with OpenGL ES 2.0
    Used vImage, vDSP, AVFoundation and related APIs to achieve real-time processing         


\section{COMPUTER SKILLS}          
    {\bf Languages}\\Proficient in: C/C++, Objective C, Python, Verilog\\
    Familiar with: Java, Ruby on Rails, JavaScript, MySQL, Scheme, SWI-Prolog\\
    {\bf Software}\\Xcode, MATLAB, Eclipse, Quartus\\
    Platforms: Microsoft Windows\textregistered, UNIX-like Operating Systems
 
\section{SCHOLARSHIP AND AWARDS}          
    \begin{tabular} {l c r}
      2008 & Ontario Scholar, Ministry of Education, Ontario & \\
      2008 & Admission Scholarship, Faculty of Applied Science and Engineering, University of Toronto & \$1000 \\
      2008 & Edward S. Rogers Scholarship & \$3000 \\
    \end{tabular}
 
\end{resume}
\end{document}
